\input{preamble}	
\raggedbottom
\begin{document}

%%% Tikz Magic %%%
\include{tikz_magi}

% Forindhold - Kun romer tal

\frontmatter

%Formalia
%\include{rapport/introduktion/main} %%%%%%%     <->    Front page, synopsis and preface included in this
\include{rapport/Start_Templates/The_Four_W}
\include{rapport/Start_Templates/Test_template}

\tableofcontents*

% Hovedindhold - nummereres fra ''side 1 af sidste side''b
\mainmatter 
\makeevenfoot{AAU}{\thepage \text{} of \pageref{LastPage}}{}{}
\makeoddfoot{AAU}{}{}{\thepage \text{} of \pageref{LastPage}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Delete this before turning in


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Include sections here   %

\include{rapport/Geo_Magic_Kinematic}
All surgical interventions with the Da Vinci robot require some sort of feedback for the user, in our work we are covering force/haptic feedback.
This type of feedback translates the forces acting on the surgical instrument to the haptic controller in some manner.
The haptic controller used in this work is the Phatnom Omni (aka Geomagic Touch) developed by Sensable Technologies.
It is one of the most cost effective haptic controllers currently on the market.

In order for useful feedback to be created, we need to be able to control the direction of the force created by the Phantom Omni.
A logical first step would be to derive the relationship between joint coordinates and end-effector position (the end-effector in this case being the point of contact between the user and device). 
Once we have this, it is possible to develop other constructs such as Jacobian and dynamic equations.

We derive the forward kinematics of the Phantom omni using the DH-algorithm for simplicity. Also, since the actuated joints only control the position, and the orientation joints are concentrated in a small space, we can separate the FK matrices into translational and rotational parts.

\begin{align}
\begin{tabular}{ |p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
 \hline
 \multicolumn{4}{|c|}{Phantom Omni DH parameters} \\
 \hline
 a &d &$\theta$ &$\alpha$ \\
 \hline
 0          & 0   &$q_{1}$&   0\\
 0          &   0           & $q_{2}$ &$\frac{\pi}{2}$\\
 A         & 0   & $q_{3}$    &  0\\
 0          & D             & $q_{4}$     & $\frac{\pi}{2}$\\
 0& 0 & $q_{5}$ &-$\frac{\pi}{2}$\\
  0& 0 & $q_{6}$ &$\frac{\pi}{2}$\\
 \hline
\end{tabular}
\end{align}



\begin{equation}
\mathbf{T_0^1} =\begin{bmatrix} \cos\theta_{1}& 0 & \sin\theta_{1} & 0\\
\sin\theta_{1}& 0 & -\cos\theta_{1} & 0\\
0 & 1 & 0 & d_{1}\\
0 & 0 & 0 & 1\\
\end{bmatrix}
\end{equation}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Bilag  %
\appendix

\clearpage

\bibliography{bibliography}

\end{document}