
%% \newacronym{label}{short name}{long name}


\newacronym{ETSC}{ETSC}{European Transport Safety Council}
\newacronym{DAA}{DAA}{Detect And Avoid}
\newacronym{MAVLINK}{MAVLINK}{Micro Air Vehicle Communication Protocol}
\newacronym{GPS}{GPS}{Global Positioning System}
\newacronym{RF}{RF}{Radio Frequency}
\newacronym{LRS}{LRS}{Laser Range Scanner}
\newacronym{UART}{UART}{Universal Asynchronous Receiver/Transmitter}
\newacronym{I2C}{$\I^2$C}{Inter Intergrated Circuit}
\newacronym{IDE}{IDE}{Intergrated Development Environment}
\newacronym{INS}{INS}{Inertial Navigation System}
\newacronym{SIO}{SIO}{Sorting Individual Objects}
\newacronym{MCU}{MCU}{Micro Controller Unit}
\newacronym{NAN}{NAN}{Not A Number}
\newacronym{ETH}{ETH Zürich}{Swiss Federal institute of Technology}
\newacronym{UAV}{UAV}{Unmanned Aerial Vehicle}
\newacronym{ADC}{ADC}{Analog to digital converter}
\newacronym{SPI}{SPI}{Serial Peripheral Interface}
\newacronym{RC}{RC}{Remote controller}





%% \newglossaryentry{label}{name={the real name}, description={robots are the better humans}}

\newglossaryentry{Liion}{name={LiPo batteries}, description={Lithium-Ion Polymer Battery are a rechargeable battery type which composition consist of lithium and iron. They are greatly used in the RC, automotive, industrial, electronics and alike. They are used because of their high power density compared to other batteries \cite{Lithium}.}}

\newglossaryentry{FM}{{name=\textit{Follow me}}, description={Describes a special feature where a drone is capable of following a target user, using a type of communication}}

\newglossaryentry{mat}{name={Matlab\textsuperscript{\textregistered}}, description={MATLAB (matrix laboratory) is a multi-paradigm numerical computing environment and fourth-generation programming language. A proprietary programming language developed by MathWorks, MATLAB allows matrix manipulations, plotting of functions and data, implementation of algorithms, creation of user interfaces, and interfacing with programs written in other languages, including C, C++, Java, Fortran and Python.}}

\newglossaryentry{concatenate}{name={concatenate}, description={In formal language theory and computer programming, string concatenation is the operation of joining character strings end-to-end. For example, the concatenation of "snow" and "ball" is "snowball"}}

\newglossaryentry{SCIP}{name={SCIP}, description={Secure Communications Interoperability Protocol is a multinational standard for secure voice and data communication. It is used for communication in land line telephone, military radios, communication satellites, Voice over IP and the several different cellular telephone standards. Therefore it was designed to make no assumptions about the underlying channel other than a minimum bandwidth of 2400 Hz\cite{SCIP2}.}}

\newglossaryentry{HASWELL}{name={Haswell}, description={Haswell is the codename for a processor microarchitecture developed by Intel as the successor to the Ivy Bridge microarchitecture. The Haswell architecture is specifically designed to optimize the power savings and performance benefits from the move to FinFET (non-planar, "3D") transistors on the improved 22 nm process node. \cite{HASWELL}.}}

\newglossaryentry{UAS}{{name={UAS}}, description={Unmaned Aircraft System is a term that covers an unmanned aircraft (UA), a ground control (GCS) / command control (C2) and the link between them. The term is therefore covering the complete system.}}


