\section{Measurement of external force at end effector} % \label{app:...}

As the Endowrist tool is highly nonlinear, measurement of how the end effector responds to external force should be made.

\subsection*{Purpose:}
To measure how external force/resistance to the end effector acts on the current consumption to the motors to contain the same position as required.

\subsection*{Test equipment:}
\begin{itemize}
\item Endowrist model 420093 (AAU number: \#4).
\item One liter water bottle with string attached.
\item Maxon 110160 motor with attached Maxon gearhead 110356 and Maxon encoder 201937.
\item Weight scale: Kern FCB 12K1 (AAU number: 86759)
\item ESCON Studio 2.2: to measure current consumption.
\end{itemize}

\subsection*{Procedure:}
The following procedure is made tree times for three different angles of the end effector on the Endowrist. The angles is chosen to be $-90^\circ$, $-0^\circ$ and $90^\circ$.
\begin{enumerate}
\item The water bottle is filled with water until a total of a 100 grams are reached. 
\item The water bottle is attached to the end of the Endowrist and the current for holding it is measured.
\item The water bottles weight is increased with 100 grams of water and the current is measured.\\
Step three and four is repeated until a total of 1000 grams is reached.


\end{enumerate}

\subsection*{Measuring data:}


\todo{Include picture of measurement (Matlab)}


\subsection*{Results:}

\subsection*{Uncertainties of measurement:}
\begin{itemize}
\item Wrong calibrated weight.
\item The attachment of the string between the end effector and the water bottle was not at the end of the end effector.
\item ESCON studio 2.2 software error.
\end{itemize}

\subsection*{Conclusion:}

