\chapter{Kinematics}\label{cha:kinematic}

From \chapref{cha:overview}, an overview of the system available on Aalborg university was introduced. In this chapter the deviation of the different kinematics are made. This is done to describe each joint and end effector positions for e.g the Geomagic touch or the Endowrist. From the positions it is possible to divert the velocity and acceleration of the joints and end effectors.

In the following the \gls{DH} notations are going to be used. This is done because it seems to be a good way of describing the kinematics as it eases the calculations of the different positions. The \gls{DH} notation only uses four parameters do describe the movement of the different joints. Each joint is given its own coordinate frame do describe the link between the different joints and are denoted as $O_i$ from 0 to $n$. To utilize the \gls{DH} notation some rules got to be fulfilled and are as followed:

\begin{itemize}
\item DH(1): The axis $x_n$ is perpendicular to axis $z_{n-1}$
\item DH(2): The axis $x_n$ intersects the axis $z_{n-1}$
\end{itemize}

furthermore the joints rotates around the z axis where the right hand rule is used.

The \gls{DH} convention is described through the transformation matrix shown in \eqref{equ:DH_trans_matrix}. This matrix is calculated for each joint and gives the transformation and rotation. Note that $sin()$ is denoted as $s$ and $cos()$ is denoted as $c$.

\begin{equation}
\begin{split}
A_i  & = Rot_{z,\theta_{i}}Trans_{z,d_{i}}Trans_{x,a_{i}}Rot_{x,\alpha_{i}} \\
     & = \begin{bmatrix}c_{\theta_{i}} & -s_{\theta_{i}} & 0 & 0 \\ s_{\theta_{i}} & c_{\theta_{i}} & 0 & 0\\  0 &0 & 1 &0 \\ 0 &0&0& 1\end{bmatrix} 
      \begin{bmatrix}1 &0& 0& 0\\ 0& 1& 0& 0\\ 0& 0& 1& d_{i}\\ 0& 0& 0& 1\end{bmatrix} 
      \begin{bmatrix} 1 & 0 &0& a_{i}\\ 0& 1& 0 &0\\ 0 &0 &1& 0\\ 0 &0& 0 &1\end{bmatrix}
      \begin{bmatrix}1& 0& 0& 0\\0& c_{\alpha_{i}}& -s_{\alpha_{i}} & 0\\ 0 & s_{\alpha_{i}} & c_{\alpha_{i}} & 0\\ 0& 0 &0& 1 \end{bmatrix}\\
     & = \begin{bmatrix}c_{\theta_i}& -s_{\theta_i}c_{\alpha_i}& s_{\theta_i}s_{\alpha_i}& a_{i}c_{\theta_i}\\ s_{\theta_i}& c_{\theta_i}c_{\alpha_i} & -c_{\theta_i}s_{\alpha_i}& a_{i}s_{\theta_i}\\ 0 & s_{\alpha_i}& c_{\alpha_i} & d_{i}\\ 0& 0& 0& 1\end{bmatrix}
\end{split}
\label{equ:DH_trans_matrix}
\end{equation}


\begin{minipage}[t]{0.20\textwidth}
Where\\
\hspace*{8mm} $a_i$ \\\\
\hspace*{8mm} $\alpha_i$ \\\\
\hspace*{8mm} $d_i$ \\\\
and \hspace*{0.7mm} $\theta_i$	
\end{minipage}
\begin{minipage}[t]{0.68\textwidth}
\vspace*{2mm}
is the distance between the axes $z_i$ and $z_{i+1}$ measured along the $x_{i+1}$ axis,\\
is the angle between the axis $z_i$ and $z_{i+1}$ measured in a plane normal to $x_{i+1}$,\\
is the distance between the origin $o_i$ and the intersection of $x_{i+1}$ axis measured along the $z_0$ axis,\\
is the angle between $x_i$ and $x_{i+1}$ measured in a plane normal to $z_0$.
\end{minipage}
\begin{minipage}[t]{0.10\textwidth}
\vspace*{2mm}
\textcolor{White}{te}$\enhed{m}$\\\\
\textcolor{White}{te}$\enhed{rad}$\\\\
\textcolor{White}{te}$\enhed{m}$\\\\
\textcolor{White}{te}$\enhed{rad}$
\end{minipage}


% a is the distance between the axes $z_i$ and $z_{i+1}$ measured along the $x_{i+1}$ axis.\\
% $\alpha$ is the angle between the axis $z_i$ and $z_{i+1}$ measured in a plane normal to $x_{i+1}$\\
% d is the distance between the origin $o_i$ and the intersection of $x_{i+1}$ axis measured along the $z_0$ axis.\\
% $\theta$ is the angle between $x_i$ and $x_{i+1}$ measured in a plane normal to $z_0$.



\input{rapport/Kinematic/Geomagic_kino.tex}

\input{rapport/Kinematic/EndoW_kino.tex}

\input{rapport/Kinematic/Da_vinci_kino.tex}